Characterization of gaps in directly bonded Si compound optics

### 2014-10-22 AO_bondedSi.tex
closes #2 (puts equation numbers on all equations)

There are two major conceivable pitfalls in Si-Si direct bonding.  The obvious pitfall is particle contamination.  Figure \ref{figParticle} shows a schematic of a particle wedged between two flat Si optical surfaces.  A single 0.6 $\mu$m particle can create a dark IR bubble from interference.  In a class 100 cleanroom, the particle volume density could be as high as $\rho=100$ particles/ft$^3$, for particle sizes larger than 0.5 $\mu$m.  What we care about is not the volume number density of particles, but the delivered surface flux $F=\rho(D) v(D)$, where $v(D)$ is the average freefall speed of particles, which is a function of particle size.  Figure 5 of Cooper 1986\cite{doi:10.1080/02786828608959094} shows the surface flux (particles cm$^{-2}$ s$^{-1}$) vs. particle size ($\mu$m).  There will be roughly $10^4$ times more 10 nm sized particles than 1 $\mu$m sized particles.  In other words:
$$\log(F) = -2\log(D) + const. \label{eqnParticleFlux}$$

@@

$$
T_{DSP} = \frac{2n}{1+n^2} \label{eqnAbsDSPtrans} \\
$$

@@

$$T_{e} = \frac{n^2+1}{2 n F \sin ^2(2\pi \frac{d}{\lambda})+n^2+1} \label{eqFP} \\$$

@@

Finally, we cascade the matrices together to compute the net transmission through the stack of abstractions.  The result is a $2\times2$ transfer matrix: $$\boldsymbol{M_{net}}=\boldsymbol{M_n}\boldsymbol{M_e}\boldsymbol{M_n}$$  From the matrix transformation equations \cite{2007fuph.book.....S} we know $M_{22}=1/T$.  Taking the inverse of the bottom right element of $\boldsymbol{M_{net}}$, we get the transmission $T_{net}$ through the net optical device:

@@

Compare equations \ref{eqn:FPmatTrans} and \ref{eq:FabPerot}.  The revised transmission has picked up a few factors of 2 and $n$.  While we are at it, let's compute the matrix for the scenario with no intermediate etalon: there are simply two Fresnel interfaces with which light interacts incoherently.  This scenario is the model for a single DSP reference puck. The revised matrix multiplication is simply $\boldsymbol{M_{DSP}}=\boldsymbol{M_n}\boldsymbol{M_n}$.  Taking the inverse of the $M_{22}$ element, we find: 
\begin{eqnarray}
T_{DSP}=\frac{2 n}{n^2+1}\label{eqn:EqofSummedSlab}
\end{eqnarray}
which is identical to the result obtained by directly summing the intensities from multiple reflections:
\begin{eqnarray}
T_{DSP}=T^2 \sum_{i=0}^{N}R^{2i} \label{eqn:multsum}
\end{eqnarray}

@@

$$
 <T_e> = \lim_{\sin^2(\delta/2) \to 0.5} \frac{1}{1+F\sin^2(\delta/2)} \\
 <T_e> = \frac{1}{1+F/2}
$$

>>>>

There are two major conceivable pitfalls in Si-Si direct bonding.  The obvious pitfall is particle contamination.  Figure \ref{figParticle} shows a schematic of a particle wedged between two flat Si optical surfaces.  A single 0.6 $\mu$m particle can create a dark IR bubble from interference.  In a class 100 cleanroom, the particle volume density could be as high as $\rho=100$ particles/ft$^3$, for particle sizes larger than 0.5 $\mu$m.  What we care about is not the volume number density of particles, but the delivered surface flux $F=\rho(D) v(D)$, where $v(D)$ is the average freefall speed of particles, which is a function of particle size.  Figure 5 of Cooper 1986\cite{doi:10.1080/02786828608959094} shows the surface flux (particles cm$^{-2}$ s$^{-1}$) vs. particle size ($\mu$m).  There will be roughly $10^4$ times more 10 nm sized particles than 1 $\mu$m sized particles.  In other words:
\begin{eqnarray}
\log(F) = -2\log(D) + const. \label{eqnParticleFlux}
\end{eqnarray}

@@

\begin{eqnarray}
T_{DSP} = \frac{2n}{1+n^2} \label{eqnAbsDSPtrans}
\end{eqnarray}

@@

\begin{eqnarray}
T_{e} = \frac{n^2+1}{2 n F \sin ^2(2\pi \frac{d}{\lambda})+n^2+1} \label{eqFP}
\end{eqnarray}

@@

Finally, we cascade the matrices together to compute the net transmission through the stack of abstractions.  The result is a $2\times2$ transfer matrix:

\begin{eqnarray}
\boldsymbol{M_{net}}=\boldsymbol{M_n}\boldsymbol{M_e}\boldsymbol{M_n}
\end{eqnarray}

From the matrix transformation equations \cite{2007fuph.book.....S} we know $M_{22}=1/T$.  Taking the inverse of the bottom right element of $\boldsymbol{M_{net}}$, we get the transmission $T_{net}$ through the net optical device:

@@

Compare equations \ref{eqn:FPmatTrans} and \ref{eq:FabPerot}.  The revised transmission has picked up a few factors of 2 and $n$.  While we are at it, let's compute the matrix for the scenario with no intermediate etalon: there are simply two Fresnel interfaces with which light interacts incoherently.  This scenario is the model for a single DSP reference puck. The revised matrix multiplication is simply $\boldsymbol{M_{DSP}}=\boldsymbol{M_n}\boldsymbol{M_n}$.  Taking the inverse of the $M_{22}$ element, we find:

\begin{eqnarray}
T_{DSP}=\frac{2 n}{n^2+1}\label{eqn:EqofSummedSlab}
\end{eqnarray}

which is identical to the result obtained by directly summing the intensities from multiple reflections:
\begin{eqnarray}
T_{DSP}=T^2 \sum_{i=0}^{N}R^{2i} \label{eqn:multsum}
\end{eqnarray}

@@

\begin{eqnarray}
 <T_e> = \lim_{\sin^2(\delta/2) \to 0.5} \frac{1}{1+F\sin^2(\delta/2)} \\
 <T_e> = \frac{1}{1+F/2}
\end{eqnarray}
